Calculating Module Enrichment and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2016-01-11 jss/article.tex
[skip ci] gbm example update

We loaded the data as a matrix in R and calculated the enrichment in ACSN maps
with the ACSNMineR function \code{enrichment}. The results are displayed in
table \ref{tab:table_gbm}. There are 16 modules significantly enriched in the
Cell Cycle, DNA repair, EMT motility and Survival. Cell matrix adhesions and ECM
(extra cellular matrix) are the modules with highest significance (corrected
p-values of 2.55e-11 and 2.34e-9 respectively). Visualization of the list of
frequently mutated genes is shown on figure \ref{fig:gbm}. This figure was
generated with the ACSNMineR commands detailed below.

@@

>>>>

We loaded the data as a matrix in R and calculated the enrichment in ACSN maps
with the ACSNMineR function \code{enrichment}. The results are displayed in
table \ref{tab:table_gbm}. There are 16 modules significantly enriched in the
Cell Cycle, DNA repair, EMT motility and Survival. Cell matrix adhesions and ECM
(extra cellular matrix), part of the EMT motility map, are the modules with
highest significance (corrected p-values of 2.55e-11 and 2.34e-9 respectively).

@@

Visualization of the list of frequently mutated genes is shown on figure
\ref{fig:gbm}. This figure was generated with the ACSNMineR commands detailed
below. Results of the enrichment test correlate well with the visualization on
the map, with a high density of low and high frequency mutated genes in the EMT
motility , survival, cell cycle and DNA repair regions (maps) of the global ACSN
map.
